%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%% Copyright 2010-2011 Mark Liu (markwayneliu@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[rpt,a4paper,sans]{moderncv}

\usepackage{verbatim}
\usepackage{fontspec}
\setmainfont{Noto Serif}
\renewcommand{\sfdefault}{\rmdefault}


% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{black}

% Remove period after lines
% See: https://tex.stackexchange.com/questions/400605/removing-periods-at-the-end-of-line-in-moderncv
\renewcommand*{\cventry}[7][.25em]{%
  \cvitem[#1]{#2}{%
    {\bfseries#3}%
    \ifthenelse{\equal{#4}{}}{}{, {\slshape#4}}%
    \ifthenelse{\equal{#5}{}}{}{, #5}%
    \ifthenelse{\equal{#6}{}}{}{, #6}%
    \strut%                             %Fullstop removed
    \ifx&#7&%
    \else{\newline{}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{2.5cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths


% personal data
\firstname{James}
\familyname{Larisch}
% \address{}{}    % optional, remove the line if not wanted
\email{james@jameslarisch.com}                      % optional, remove the line if not wanted
\homepage{https://jameslarisch.com/}                % optional, remove the line if not wanted
%\extrainfo{\url{http://markliu.me}} % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Education}
\cventry{2017--2024}{PhD, Computer Science}{Harvard University}{Cambridge, MA}{}{}
\cvline{}{\small Advisor: Eddie Kohler}
\cvline{}{\small Committee: Eddie Kohler, Minlan Yu, Stephen Chong, Christo
Wilson}
\cventry{2017--2020}{MS, Computer Science}{Harvard University}{Cambridge, MA}{}{}
\cvline{}{\small Advisor: James Mickens}
\cventry{2012--2017}{BS, Computer Science}{Northeastern University}{Boston, MA}{}{}  % arguments 3 to 6 can be left empty
\cvline{}{\small Magna Cum Laude}
\cvline{}{\small With Honors}

\section{Honors \& Awards}
\cventry{2022}{Honorable Mention - Best Paper - Hammurabi}{ACM CCS 2022}{}{}{}
\cventry{2019}{NSF Graduate Research Fellowship}{National Science Foundation}{}{}{}
\cventry{2017}{Chen Graduate Student Research Fellowship}{Harvard University}{}{}{}
\cventry{2017}{IEEE Cybersecurity Award for Innovation - CRLite}{IEEE SecDev 2017 \& MITRE}{}{}{}
\cventry{2017}{Undergraduate Research Award}{Northeastern University, CCIS}{}{}{}
\cventry{2012}{Fellows Scholarship}{Northeastern University, CCIS}{}{}{}
\cventry{2012}{Excellence Scholarship}{Northeastern University}{}{}{}

% \section{Current Research}
%
% \cvline{In Progress}{\textbf{James Larisch}, Eric Lu, Alisha Ukani,
% Gabriele Oliaro, Savvy Raghuvanshi,
% Jeremy Hsu,
% Stephen Herwig,
%   Eddie Kohler, and James Mickens. ``\textbf{Juice:
%   Stateful Serverless Functions without Manually Persisted State}.''}

\section{Refereed Publications}

\cvline{SIGCOMM 2024}{\textbf{James Larisch}, Timothy Alberdingk-Thijm, Suleman Ahmad,
  Peter Wu, Tom Arnfeld, and Marwan Fayed.
  ``\textbf{Topaz: Declarative and Verifiable Authoritative DNS at CDN-Scale.}'' In ACM Special Interest Group on Data Communication (SIGCOMM). 2024.}{}{}{}{}

\cvline{HotNets 2023}{\textbf{James Larisch}, Waqar Aqeel, Taejoong Chung,
  Eddie Kohler, Dave Levin, Bruce M. Maggs, Bryan Parno, and Christo Wilson.
  ``\textbf{No Root Store Left Behind}'' In ACM Workshop on Hot Topics in Networks (HotNets). 2023.}{}{}{}{}

\cvline{CCS 2022}{\textbf{James Larisch}, Waqar Aqeel, Michael Lum,
  Yaelle Goldschlag, Kasra Torshizi, Leah Kannan, Yujie Wang, Taejoong Chung,
  Dave Levin, Bruce M. Maggs,
  Alan Mislove, Bryan Parno, and Christo Wilson. ``\textbf{Hammurabi: A Framework
  for Pluggable, Logic-Based X.509 Certificate Validation Policies.}'' In ACM
  SIGSAC Conference on Computer and Communications Security (CCS). 2022.}{}{}{}{}

\cvline{FCS 2020}{Waqar Aqeel, Zachary Hanif, \textbf{James Larisch}, Olamide Omolola,
  Mislove, and Christo Wilson. ``\textbf{CRLite: A Scalable System for Pushing All TLS
  Revocations to All Browsers.}'' In 2017 IEEE Symposium on Security and Privacy
  (SP), pp. 539--556. IEEE, 2017.}{}{}{}{}

\cvline{ManLang 2018}{\textbf{James Larisch}, James Mickens, and Eddie Kohler. ``\textbf{Alto:
  Lightweight VMs Using Virtualization-aware Managed Runtimes.}'' In Proceedings
  of the 15th International Conference on Managed Languages \& Runtimes, pp. 1--7. 2018.}{}{}{}{}

\cvline{Oakland 2017}{\textbf{James Larisch}, David Choffnes, Dave Levin, Bruce M. Maggs, Alan
  Mislove, and Christo Wilson. ``\textbf{CRLite: A Scalable System for Pushing All TLS
  Revocations to All Browsers.}'' In 2017 IEEE Symposium on Security and Privacy
  (SP), pp. 539--556. IEEE, 2017.}{}{}{}{}

\section{Research Adoption \& Coverage}

\cvline{2024}{How we prevent conflicts in authoritative DNS configuration using
formal verification. \emph{Cloudflare Blog.}}

\cvline{2020}{Introducing CRLite: All of the Web PKI’s revocations,
compressed. \emph{Mozilla Security Blog.}}


\section{Teaching \& Mentoring}

\cventry{2022-2023}{InTouch Peer}{InTouch Peer-to-Peer Student Support
Group}{Harvard}{}{}

\cventry{2020}{Undergraduate Research Mentor}{Harvard Women in Computer Science}{Systems Group}{}{}
\cventry{Fall 2018}{Teaching Fellow}{CS263: Systems Security}{James Mickens}{}{}

\section{Work Experience}

\cventry{2024-Present}{Research Engineer}{Cloudflare}{Remote}{}{}
\cvline{}{Designed and deployed new DNS edge microservice in Go that handles over 1M requests per second globally.}
\cvline{}{Invented new Lisp-based programming language that reduces deployment time of DNS changes by over 100x.}
\cvline{}{Formally verified all DNS changes using Racket, which prevents 1-3 network incidents a month.}

\cventry{2021-2022}{Research Engineer Intern}{Cloudflare}{Remote}{}{}
% \cvline{}{- Developed a new DNS subsystem (details to come).}

\cventry{2016}{Software Engineer Co-op}{Sonian}{Waltham, MA}{}{}
\cvline{}{Reduced incident debugging time from hours to minutes by
creating the company's first request-tracing system.}

\cventry{2015}{Software Engineer Co-op}{Gem.co}{Los Angeles, CA}{}{}
%\cvline{}{Back-end engineer. Tech: Ruby, PostgreSQL, Bitcoin.}
\cvline{}{Deployed webhook API product, which sent HTTP requests
to customer endpoints upon Bitcoin blockchain events.}
\cvline{}{
  Reduced blockchain data retrieval times by 2x by forking and running
  a modified Bitcoin node instance in Ruby.}

\cventry{2014}{Software Engineer Co-op}{HubSpot}{Cambridge, MA}{}{}
\cvline{}{Reduced analytics event processing time from 60-90m to 5-15s
by converting bloated Hadoop pipeline to Kafka.}
\cvline{}{Designed traffic simulation tool using Java
that prevented a major analytics incident months before it
happened.}

\cventry{2013}{Software Engineer}{Focused Coaching}{Morganville, NJ}{}{}
\cvline{}{- Sole developer of online SAT score aggregation platform written using Ruby-on-Rails.}

% \section{Technical Skills}
% \cvline{proficient}{Go, Ruby, Rust, Java}
% \cvline{experienced}{C, Lua, C++, OCaml, Haskell, Prolog,
% JavaScript, SQL, Python, Racket, TypeScript}
%
\section{Community}

\cventry{2018}{Technical Advisory Volunteer}{ACLU Massachusetts}{}{}{}{}
\cvline{}{Demystified privacy and security concerns at community ``Crypto
  Parties''.}

\cventry{2018}{Technical Mentor}{YouthCITIES}{}{}{}{}
\cvline{}{Mentored high school students building healthcare-focused startup
  prototypes.}

% \section{Part-Time Work Experience}
%
% \cventry{2019--2020}{Senior Interview Engineer}{Karat.io}{Remote}{}{}
% \cvline{}{- Conducted over 30 hour-long technical interviews with software
%   engineering candidates.}
% \cvline{}{- Completed comprehensive evaluation write-ups for each candidate.}
%
% \cventry{2017}{Technical Lead}{Soli}{Boston, MA}{}{}
% \cvline{}{- Designed and implemented NodeJS back-end for mobile-only,
% early-stage startup.}
% \cvline{}{- Interviewed and hired the company's CTO.}

%\section{Technical Proficiency}
%\subsection{Proficient With}
%\cvline{languages}{Go, Ruby, Java, C, Javascript, HTML, CSS}
%\subsection{Have Experience With}
%\cvline{languages}{Rust, C++, Clojure, Racket, Haskell, OCaml, Python}
%\cvline{technologies}{Apache Hadoop, Apache Kafka, Apache }


\end{document}
